---
title: "Assignment2"
author: "Ersan Kucukoglu"
date: "11/29/2021"
output:
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#clear memory
rm(list=ls())
#load the libraries
library(tidyverse)
library(httr)
library(jsonlite)
library(data.table)
library(kableExtra)
library(modelsummary)
```
### API Data Processing

[Covid Act Now](https://covidactnow.org/?s=26091515) 

[API](https://apidocs.covidactnow.org/)

The Covid Act Now API provides access to all of our COVID data tracking US states, counties, and metros.

It includes data and metrics for cases, vaccinations, tests, hospitalizations, and deaths. See data definitions for all included data.

The API provides the same data that powers Covid Act Now but in easily digestible CSV or JSON files, intended for consumption by other COVID websites, models, and tools.


```{r,echo=FALSE}
#base url
base <- 'https://api.covidactnow.org/v2/county/'

info_key <- '.timeseries.json?apiKey=f6426572c2ad47848dedfecccad1de97'
```

```{r,echo=FALSE}
#  GET request for the first API
county <- '06037'
API_URL <- paste0(base, county, info_key)
api_call <- GET(API_URL)
#api_call$status_code
#api_call$content

# Converting the content of the API pull into a list
api_json <- fromJSON(rawToChar(api_call$content), flatten = TRUE)

df <- api_json$actualsTimeseries
```


### Functions, lapply and rbindlist
```{r}

# Taking the three counties; Los Angeles, San Diego, San Francisco
counties <- c('06037', '06073', '06075')

#List of API urls for each county
API_urls <- paste0(base,counties[1:3],info_key)

# Get the multiple API data
get_API_data <- function(API) {
  api_call <- GET(API)
  
  api_json <- fromJSON(rawToChar(api_call$content), flatten = TRUE) 
  df1 <- api_json$actualsTimeseries
}
#list of dfs
list_of_dfs <- lapply(API_urls, get_API_data)
#final df
final_df <- rbindlist(list_of_dfs)

```

### Head of the resul
```{r,echo=FALSE}
final_df <- final_df %>% filter(!is.na(cases ))
final_df$date <- as.Date(final_df$date)
final_df$county <- NA
LA <- final_df$county[1:666] <-"Los Angeles"
SD <- final_df$county[666:1317] <-"San Diego"
SF <- final_df$county[1317:1976] <-"San Francisco"
# Looking at the top rows for a few specific columns
kbl(head(final_df[,c("cases", "deaths", "newCases","newDeaths","date")],10))
```

```{r,echo=FALSE,warning=FALSE}
p1 <- ggplot(data=final_df %>% filter(date >= "2021-01-01"),aes(x=date, y=newDeaths,color=county))+
  geom_line()+
  labs(title = "New Deaths after 2021-01-01 in Los Angeles,San Diego,San Francisco",x= "Date", y= "New Confirmed Deaths")
  
p1

```

```{r, echo=FALSE,warning=FALSE}
p2 <- ggplot(final_df %>% filter(!is.na(cases ) & !is.na(deaths) & date >= "2021-01-01"),aes(x=cases,y=deaths,color=county))+
  geom_line()+
  labs(title='Cases vs. Deaths after 2021-01-01 in Los Angeles,San Diego,San Francisco ',x='Cases',y='Deaths')
p2

```

